\pkg{casebase}: An Alternative Framework For Survival Analysis and Comparison of Event Rates

### 2021-11-04 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.Rmd
add section on approximate bayes

@@

Finally, the output from \code{absoluteRisk} can be passed to a method \code{confint} to compute confidence bands around the survival function. These bands are computed using parametric bootstrap, and therefore are only valid when \code{family = "glm"} as it relies on the asymptotic normality of the estimator. Currently, this is only available for the single-event setting.

@@

These point-wise confidence intervals are constructed using parametric bootstrap; 
the validity of this approach relies on the asymptotic normality of the MLE. In Figure \ref{fig:erspc-cif-conf}, we see the 95% confidence bands around the estimates. 
We also overlay the Kaplan-Meier curves as a reference.

>>>>

## Variance estimates

The asymptotic normality of $\hat{\theta}$ gives us an efficient way to estimate the variance of various estimators derived from the hazard function. For example, to construct confidence bands around risk functions and survival functions, we can use the following procedure:

  1. Compute $\hat{\theta}$ and its variance-covariance matrix $V(\theta)$.
  2. Sample $B$ times from a multivariate normal $N\left(\hat{\theta}, V(\theta)\right)$.
  3. For each sample, compute the survival function using Equation \ref{eqn:surv} below.
  4. Use the pointwise quantiles of these survival function estimates to construct a pointwise confidence band for the survival function.

This procedure is similar to parametric bootstrap [@efron1994introduction, Section 6.5], but it can be more accurately described as a form of approximate Bayesian computation. As such, the validity of the confidence bands relies on the Bernstein-von Mises theorem [@van2000asymptotic, Chapter 10].

@@

Finally, the output from \code{absoluteRisk} can be passed to a method \code{confint} to compute confidence bands around the survival function, as described in the Theoretical Details section. These bands are only valid when \code{family = "glm"} as it relies on the asymptotic normality of the estimator. Currently, this is only available for the single-event setting.

@@

In Figure \ref{fig:erspc-cif-conf}, we see the 95% confidence bands around the estimates. 
We also overlay the Kaplan-Meier curves as a reference.

### 2021-11-04 analysis/paper/bhatnagar-turgeon-islam-hanley-saarela.tex
add section on approximate bayes

@@

These point-wise confidence intervals are constructed using parametric
bootstrap; the validity of this approach relies on the asymptotic
normality of the MLE. In Figure \ref{fig:erspc-cif-conf}, we see the
95\% confidence bands around the estimates. We also overlay the
Kaplan-Meier curves as a reference.

>>>>

\hypertarget{variance-estimates}{%
\subsection{Variance estimates}\label{variance-estimates}}

The asymptotic normality of \(\hat{\theta}\) gives us an efficient way
to estimate the variance of various estimators derived from the hazard
function. For example, to construct confidence bands around risk
functions and survival functions, we can use the following procedure:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compute \(\hat{\theta}\) and its variance-covariance matrix
  \(V(\theta)\).
\item
  Sample \(B\) times from a multivariate normal
  \(N\left(\hat{\theta}, V(\theta)\right)\).
\item
  For each sample, compute the survival function using Equation
  \ref{eqn:surv} below.
\item
  Use the pointwise quantiles of these survival function estimates to
  construct a pointwise confidence band for the survival function.
\end{enumerate}

This procedure is similar to parametric bootstrap \citep[Section
6.5]{efron1994introduction}, but it can be more accurately described as
a form of approximate Bayesian computation. As such, the validity of the
confidence bands relies on the Bernstein-von Mises theorem
\citep[Chapter 10]{van2000asymptotic}.

@@

In Figure \ref{fig:erspc-cif-conf}, we see the 95\% confidence bands
around the estimates. We also overlay the Kaplan-Meier curves as a
reference.
